---
title: 'Creating Custom Reporting Functions in RMD'
author: Melissa Phillips
date: October, 2024
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: zenburn
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide')
library( tidyverse )
library( fontawesome )

```
# Custom Reporting Functions

Below, we detail how to convert the following [R Epidemics Member Gallery](https://www.repidemicsconsortium.org/people/) into RMD format by replicating the existing gallery template using a custom R function to build the duplicate gallery. 

## Step 1: Create a New RMD File

Create a new RMD file using the below YAML settings. 


```{r, eval=FALSE}
---
title: 'Page Title'
output:
   html_document:
     theme: readable
     df_print: paged
     highlight: zenburn
     toc: true
---
```

## Step 2: Member Data Frame 

Create a data frame for members with vectors for each information type (WEBSITE, NAME, etc) and manually add items for team members and use an empty string as a placeholder ("") if a member is missing information in one of the fields. 
<br>
<br>
Bind the vectors together into a data frame using `data.frame()` function. 

```{r}

member_list <- list(
                    FIRST_NAME = c("Cici",
                                   "Matthijs",
                                   "Mahendra",
                                   "Sangeeta"),
                    LAST_NAME = c("Bauer", 
                                  "Berends", 
                                  "Bhandari", 
                                  "Bhatia"),
                    WEBSITE = c( "https://cicibauer.netlify.com/", 
                            "https://www.rug.nl/staff/m.s.berends/",
                            "https://%20www.ainqa.com/", 
                            "https://sangeetabhatia03.github.io/"),
                    IMG = c( "https://raw.githubusercontent.com/Watts-College/paf-514-template/main/labs/images/avatar-01.png", 
                             "https://raw.githubusercontent.com/Watts-College/paf-514-template/main/labs/images/avatar-02.png", 
                             "https://raw.githubusercontent.com/Watts-College/paf-514-template/main/labs/images/avatar-03.png", 
                             "https://raw.githubusercontent.com/Watts-College/paf-514-template/main/labs/images/avatar-04.png"),
                    DESC = c("Academic faculty (assistant professor) - Bayesian spatiotemporal modeling, Department of Biostatistics and Data Science, University of Texas Health Science Center in Houston, United States",
                             "Infectious Disease Epidemiology, University of Groningen, Netherlands", 
                             "Head Intelligent Automation , Predictive Modelling , Ensemble Forecast , Location Based Intelligence , Python / R, AINQA, India", 
                             "Modeller and software developer contributing packages for outbreak analysis using digital surveillance data., Imperial College London, UK., NA"),
                    GITHUB = c( "https://github.com/cicibauer", 
                                "https://github.com/msberends", 
                                "", 
                              "https://github.com/sangeetabhatia03"), 
                    TWITTER = c("", 
                                "https://twitter.com/msberends", 
                                "",
                                "https://twitter.com/sangeeta0312")
                    )
# Create Member Data Frame
member_df <- as.data.frame(member_list)

# Create combined name column
member_df$NAME <- paste(member_df$FIRST_NAME, member_df$LAST_NAME)

# Move combined name column to font of data set
member_df <- member_df %>% 
                select(NAME, everything())

# Sort df by last name
member_df <- member_df[order(member_df$LAST_NAME),]

print(member_df)
                         
```

### Useful HTML with variables

<div class="list-circles-item">

	<a href="WEBSITE"><img src="IMG" class="item-img"></a>

	<h4 class="item-name">NAME</h4>
	<div class="item-desc">DESC</div>

	<div class="item-links">

	   <a class="item-link" href="WEBSITE" title="Website">
	   <svg><path d="..."/></svg>   /* --- abbreviated fa.home svg --- */
	   </a>

	   <a class="item-link" href="GITHUB" title="GitHub">
	   <svg><path d="..."/></svg>   /* --- abbreviated fa.github svg --- */
	   </a>

	   <a class="item-link" href="TWITTER" title="Twitter">
	   <svg><path d="..."/></svg>   /* --- abbreviated fa.twitter svg --- */
	   </a>

	</div>

</div>

## Step 3: Build_circle Function

Write an R function called build_circle() that will create a single member profile for the team gallery page.

### Member Elements: 

- WEBSITE - personal website URL
- IMG - full URL of profile photo of a team member
- NAME - team member full name
- DESC - one sentence bio
- GITHUB - URL of personal GitHub page
- TWITTER - Twitter URL

```{r}
# build_circle function

build_circle <- function(WEBSITE="", IMG="", NAME="", DESC="", GITHUB="", TWITTER="")
  {
    
  # beginning of code
  cat( '<div class="list-circles-item">')
  cat( '\n') # line break
  cat( '\n') # line break
  
  # member name & image
  if (WEBSITE != ""){
  cat( paste0(' <a href="', WEBSITE, '">') )
  cat( '\n')  
  cat( paste0(' <img src="', IMG, '" class="item-img"></a>') )
  } else {
    cat( paste0(' <img src="', IMG, '" class="item-img">') )
  }
  cat( '\n') 
  cat( '\n') 
  if (NAME != ""){
  cat( paste0(' <h4 class="item-name">', NAME, '</h4>') )
  } 
  cat( '\n') 
   
  # description
  if(DESC != ""){
  cat( paste0('  <div class="item-desc">',  DESC,'</div>'))
  } else {
  cat( paste0('  <div class="item-desc">',  "Bio coming soon!",'</div>'))
  }
  cat( '\n')  
  cat( '\n') 
  
  # links / fontawesome icons
  cat( '   <div class="item-links">')
  cat( '\n') 
  cat( '\n') 
  
  ## home page
  if(WEBSITE != ""){
  cat( paste0('   <a class=item-link" href="', WEBSITE, '" title="Website">'), fontawesome::fa(name="home"), '</a>' )
  cat( '\n') 
  cat( '\n') 
  }
  
  ## github
  if(GITHUB != ""){
  cat( paste0('   <a class=item-link" href="', GITHUB, '" title="Github">'), fontawesome::fa(name="github"), '</a>' )
  cat( '\n') 
  cat( '\n') 
  }
  
  ##twitter
  if(TWITTER != ""){
  cat( paste0('   <a class=item-link" href="', TWITTER, '" title="Twitter">'), fontawesome::fa(name="twitter"), '</a>' )
  cat( '\n') 
  cat( '\n') 
  }
  cat( '   </div>')
  
  # end of code
  cat( '\n') 
  cat( '\n') 
  cat('</div>')
}
```


## Step 4: Loop Through R Epidemics Consortium Members

Create a loop to generate profile sections for team members using `cat()` function. 

```{r, results='asis', echo=FALSE}
# Create report
# For loops allow us to rotate through all our members

cat( '<div class="list-circles">' )
cat( '\n' )  # line break 
cat( '\n' )  # line break

for (i in 1:nrow(member_df)) {
   df <- member_df[ i , ] # select one row (one team member) 
   build_circle( WEBSITE=df$WEBSITE,
     IMG=df$IMG,
     NAME=df$NAME,
     DESC=df$DESC,
     GITHUB=df$GITHUB,
     TWITTER=df$TWITTER  )
  cat( '\n' )  # line break 
  cat( '\n' )  # line break
}
cat( '</div>' )
```
## Step 5: Add Custom CSS to Replicate Gallery Style

Adding list-circles CSS items to RMD code to stylize elements. 

```{css, eval=FALSE}
<style>
/* --- css elements here --- */
/* --- Lists of circles --- */

div { display: block } 
  
.list-circles {
  text-align: center;
}

@media only screen and (min-width: 1200px) {
  .list-circles {
    width: 150%;
    margin-left: -25%;
  }
}


.list-circles-item {
  display: inline-block;
  width: 240px;
  vertical-align: top;
  margin: 0;
  padding: 20px;
}

.list-circles-item:hover {
  background: #fafafa;
}

.list-circles-item .item-img {
  max-width: 200px;
  height: 200px;
  -webkit-border-radius: 50%;
  -moz-border-radius: 50%;
  border-radius: 50%;
  border: 1px solid #777;
}

.list-circles-item .item-desc {
  font-size: 16px;
  font-family: 'Open Sans', 'Helvetica Neue', Helvetica, Arial, sans-serif;
}

.list-circles-item .item-links {
  margin-top: 10px;
  padding-right: 5px;
  display: flex; 
  justify-content: center; 
  align-items: center;
}

.list-circles-item .item-link {
  margin:0 3px;
  color: #314f96;
  text-decoration: none !important;
  padding-right: 10px;
  padding-left: 10px;
}

.list-circles-item .item-link:hover {
  color: #042265;
}

.svg-icon {
  display: inline-flex;
  align-self: center;
}
</style>
```
```{css, echo=FALSE}
<style>
/* --- css elements here --- */
/* --- Lists of circles --- */

div { display: block } 
  
.list-circles {
  text-align: center;
}

@media only screen and (min-width: 1200px) {
  .list-circles {
    width: 150%;
    margin-left: -25%;
  }
}


.list-circles-item {
  display: inline-block;
  width: 240px;
  vertical-align: top;
  margin: 0;
  padding: 20px;
}

.list-circles-item:hover {
  background: #fafafa;
}

.list-circles-item .item-img {
  max-width: 200px;
  height: 200px;
  -webkit-border-radius: 50%;
  -moz-border-radius: 50%;
  border-radius: 50%;
  border: 1px solid #777;
}

.list-circles-item .item-desc {
  font-size: 16px;
  font-family: 'Open Sans', 'Helvetica Neue', Helvetica, Arial, sans-serif;
}

.list-circles-item .item-links {
  margin-top: 10px;
  padding-right: 5px;
  display: flex; 
  justify-content: center; 
  align-items: center;
}

.list-circles-item .item-link {
  margin:0 3px;
  color: #314f96;
  text-decoration: none !important;
  padding-right: 10px;
  padding-left: 10px;
}

.list-circles-item .item-link:hover {
  color: #042265;
}

.svg-icon {
  display: inline-flex;
  align-self: center;
}
</style>
```
